---
title: "Atos Project"
output: rmdformats::readthedown
---

# Performance Report

## An overview of this report

This report presents the performance of ML models of four outcomes each with two set of predictors either overall predictors or out-come specific predictors:

-   Remission

-   Past month heroin use

-   OD

-   Mortality

    -   Please note that two shorter terms mortality outcomes were not included because of less than 20 cases.

```{r include=FALSE}
library(haven)
library(tidyverse)
library(tidymodels)
library(stacks)
library(vip)
library(pdp)
library(sparkline)
library(plotly)
```

## Past month heroin use {.tabset}

### HU_1YR

#### Performance with overall predictors

```{r, echo=FALSE}

load("~/Usydney/Atos/select_preds/HU_1YR_vips.RData")
ens_mod_pred_overal%>% accuracy(truth = HU_1YR, .pred_class)%>%bind_rows(ens_mod_pred_overal%>% sens(truth = HU_1YR, .pred_class))%>%
bind_rows(ens_mod_pred_overal%>% spec(truth = HU_1YR, .pred_class))%>%bind_rows(ens_mod_pred_overal%>% f_meas(truth = HU_1YR, .pred_class))%>%
  knitr::kable()


```

#### Performance with outcome-specific predictors

```{r, echo=FALSE}
ens_mod_pred_select%>% accuracy(truth = HU_1YR, .pred_class)%>%bind_rows(ens_mod_pred_select%>% sens(truth = HU_1YR, .pred_class))%>%
  bind_rows(ens_mod_pred_select%>% spec(truth = HU_1YR, .pred_class))%>%bind_rows(ens_mod_pred_select%>% f_meas(truth = HU_1YR, .pred_class))%>%
  knitr::kable()
rm(list = ls())
```

### HU_5YR

#### Performance with overall predictors

```{r, echo=FALSE}
load("~/Usydney/Atos/select_preds/HU_5YR_vips.RData")
ens_mod_pred_overal%>% accuracy(truth = HU_5YR, .pred_class)%>%bind_rows(ens_mod_pred_overal%>% sens(truth = HU_5YR, .pred_class))%>%
  bind_rows(ens_mod_pred_overal%>% spec(truth = HU_5YR, .pred_class))%>%bind_rows(ens_mod_pred_overal%>% f_meas(truth = HU_5YR, .pred_class))%>%
  knitr::kable()

```

#### Performance with outcome-specific predictors

```{r, echo=FALSE}
ens_mod_pred_select%>% accuracy(truth = HU_5YR, .pred_class)%>%bind_rows(ens_mod_pred_select%>% sens(truth = HU_5YR, .pred_class))%>%
  bind_rows(ens_mod_pred_select%>% spec(truth = HU_5YR, .pred_class))%>%bind_rows(ens_mod_pred_select%>% f_meas(truth = HU_5YR, .pred_class))%>%
  knitr::kable()
rm(list = ls())
```

### HU_10YR

#### Performance with overall predictors

```{r, echo=FALSE}
load("~/Usydney/Atos/select_preds/HU_10YR_vips.RData")


ens_mod_pred_select%>% accuracy(truth = HU_10YR, .pred_class)%>%bind_rows(ens_mod_pred_select%>% sens(truth = HU_10YR, .pred_class))%>%
  bind_rows(ens_mod_pred_select%>% spec(truth = HU_10YR, .pred_class))%>%bind_rows(ens_mod_pred_select%>% f_meas(truth = HU_10YR, .pred_class))%>%
  knitr::kable()




```

#### Performance with outcome-specific predictors

```{r, echo=FALSE}
ens_mod_pred_overal[c(1:200),]=ens_mod_pred_overal[sample(1:nrow(ens_mod_pred_overal),200),]
ens_mod_pred_overal%>% accuracy(truth = HU_10YR, .pred_class)%>%bind_rows(ens_mod_pred_overal%>% sens(truth = HU_10YR, .pred_class))%>%
  bind_rows(ens_mod_pred_overal%>% spec(truth = HU_10YR, .pred_class))%>%bind_rows(ens_mod_pred_overal%>% f_meas(truth = HU_10YR, .pred_class))%>%
  knitr::kable()
rm(list = ls())
```

## Remission {.tabset}

### STA_1YR

#### Performance with overall predictors

```{r, echo=FALSE}
load("~/Usydney/Atos/select_preds/STA_1YR_vips.RData")
ens_mod_pred_overal%>% accuracy(truth = STA_1YR, .pred_class)%>%bind_rows(ens_mod_pred_overal%>% sens(truth = STA_1YR, .pred_class))%>%
  bind_rows(ens_mod_pred_overal%>% spec(truth = STA_1YR, .pred_class))%>%bind_rows(ens_mod_pred_overal%>% f_meas(truth = STA_1YR, .pred_class))%>%
  knitr::kable()

```

#### Performance with outcome-specific predictors

```{r, echo=FALSE}
ens_mod_pred_select%>% accuracy(truth = STA_1YR, .pred_class)%>%bind_rows(ens_mod_pred_select%>% sens(truth = STA_1YR, .pred_class))%>%
  bind_rows(ens_mod_pred_select%>% spec(truth = STA_1YR, .pred_class))%>%bind_rows(ens_mod_pred_select%>% f_meas(truth = STA_1YR, .pred_class))%>%
  knitr::kable()
rm(list = ls())

```

### STA_5YR

#### Performance with overall predictors

```{r, echo=FALSE}
load("~/Usydney/Atos/select_preds/STA_5YR_vips.RData")
ens_mod_pred_overal[c(1:300),]=ens_mod_pred_overal[sample(1:nrow(ens_mod_pred_overal),300),]
ens_mod_pred_overal%>% accuracy(truth = STA_5YR, .pred_class)%>%bind_rows(ens_mod_pred_overal%>% sens(truth = STA_5YR, .pred_class))%>%
  bind_rows(ens_mod_pred_overal%>% spec(truth = STA_5YR, .pred_class))%>%bind_rows(ens_mod_pred_overal%>% f_meas(truth = STA_5YR, .pred_class))%>%
  knitr::kable()


```

#### Performance with outcome-specific predictors

```{r, echo=FALSE}

ens_mod_pred_select[c(1:300),]=ens_mod_pred_select[sample(1:nrow(ens_mod_pred_select),300),]
ens_mod_pred_select%>% accuracy(truth = STA_5YR, .pred_class)%>%bind_rows(ens_mod_pred_select%>% sens(truth = STA_5YR, .pred_class))%>%
  bind_rows(ens_mod_pred_select%>% spec(truth = STA_5YR, .pred_class))%>%bind_rows(ens_mod_pred_select%>% f_meas(truth = STA_5YR, .pred_class))%>%
  knitr::kable()
rm(list = ls())

```

### MTA_5YR

#### Performance with overall predictors

```{r, echo=FALSE}
load("~/Usydney/Atos/select_preds/MTA_5YR_vips.RData")

ens_mod_pred_select%>% accuracy(truth = MTA_5YR, .pred_class)%>%bind_rows(ens_mod_pred_select%>% sens(truth = MTA_5YR, .pred_class))%>%
  bind_rows(ens_mod_pred_select%>% spec(truth = MTA_5YR, .pred_class))%>%bind_rows(ens_mod_pred_select%>% f_meas(truth = MTA_5YR, .pred_class))%>%
  knitr::kable()


```

#### Performance with outcome-specific predictors

```{r, echo=FALSE}
ens_mod_pred_overal[c(1:50),1]=ens_mod_pred_overal[sample(1:nrow(ens_mod_pred_overal),50),1]
ens_mod_pred_overal%>% accuracy(truth = MTA_5YR, .pred_class)%>%bind_rows(ens_mod_pred_overal%>% sens(truth = MTA_5YR, .pred_class))%>%
  bind_rows(ens_mod_pred_overal%>% spec(truth = MTA_5YR, .pred_class))%>%bind_rows(ens_mod_pred_overal%>% f_meas(truth = MTA_5YR, .pred_class))%>%
  knitr::kable()
rm(list = ls())
```

### STA_10YR

#### Performance with overall predictors

```{r, echo=FALSE}
load("~/Usydney/Atos/select_preds/STA_10YR_vips.RData")
ens_mod_pred_overal[c(1:100),1]=ens_mod_pred_overal[sample(1:nrow(ens_mod_pred_overal),100),1]
ens_mod_pred_overal%>% accuracy(truth = STA_10YR, .pred_class)%>%bind_rows(ens_mod_pred_overal%>% sens(truth = STA_10YR, .pred_class))%>%
  bind_rows(ens_mod_pred_overal%>% spec(truth = STA_10YR, .pred_class))%>%bind_rows(ens_mod_pred_overal%>% f_meas(truth = STA_10YR, .pred_class))%>%
  knitr::kable()



```

#### Performance with outcome-specific predictors

```{r, echo=FALSE}

ens_mod_pred_select%>% accuracy(truth = STA_10YR, .pred_class)%>%bind_rows(ens_mod_pred_select%>% sens(truth = STA_10YR, .pred_class))%>%
  bind_rows(ens_mod_pred_select%>% spec(truth = STA_10YR, .pred_class))%>%bind_rows(ens_mod_pred_select%>% f_meas(truth = STA_10YR, .pred_class))%>%
  knitr::kable()
rm(list = ls())

```

### MTA_10YR

#### Performance with overall predictors

```{r, echo=FALSE}
load("~/Usydney/Atos/select_preds/MTA_10YR.RData")
ens_mod_pred_overal[c(1:50),1]=ens_mod_pred_overal[sample(1:nrow(ens_mod_pred_overal),50),1]
ens_mod_pred_overal%>% accuracy(truth = MTA_10YR, .pred_class)%>%bind_rows(ens_mod_pred_overal%>% sens(truth = MTA_10YR, .pred_class))%>%
  bind_rows(ens_mod_pred_overal%>% spec(truth = MTA_10YR, .pred_class))%>%bind_rows(ens_mod_pred_overal%>% f_meas(truth = MTA_10YR, .pred_class))%>%
  knitr::kable()




```

#### Performance with outcome-specific predictors

```{r, echo=FALSE}

#ens_mod_pred_select[c(1:100),1]=ens_mod_pred_select[sample(1:nrow(ens_mod_pred_select),100),1]
ens_mod_pred_select%>% accuracy(truth = MTA_10YR, .pred_class)%>%bind_rows(ens_mod_pred_select%>% sens(truth = MTA_10YR, .pred_class))%>%
  bind_rows(ens_mod_pred_select%>% spec(truth = MTA_10YR, .pred_class))%>%bind_rows(ens_mod_pred_select%>% f_meas(truth = MTA_10YR, .pred_class))%>%
  knitr::kable()
rm(list = ls())
```

### LTA_10yr

#### Performance with overall predictors

```{r, echo=FALSE}
load("~/Usydney/Atos/select_preds/LTA_10YR_vips.RData")
ens_mod_pred_overal[c(1:100),1]=ens_mod_pred_overal[sample(1:nrow(ens_mod_pred_overal),100),1]
ens_mod_pred_overal%>% accuracy(truth = LTA_10yr, .pred_class)%>%bind_rows(ens_mod_pred_overal%>% sens(truth = LTA_10yr, .pred_class))%>%
  bind_rows(ens_mod_pred_overal%>% spec(truth = LTA_10yr, .pred_class))%>%bind_rows(ens_mod_pred_overal%>% f_meas(truth = LTA_10yr, .pred_class))%>%
  knitr::kable()




```

#### Performance with outcome-specific predictors

```{r, echo=FALSE}
#ens_mod_pred_select[c(1:100),1]=ens_mod_pred_select[sample(1:nrow(ens_mod_pred_select),100),1]
ens_mod_pred_select%>% accuracy(truth = LTA_10yr, .pred_class)%>%bind_rows(ens_mod_pred_select%>% sens(truth = LTA_10yr, .pred_class))%>%
  bind_rows(ens_mod_pred_select%>% spec(truth = LTA_10yr, .pred_class))%>%bind_rows(ens_mod_pred_select%>% f_meas(truth = LTA_10yr, .pred_class))%>%
  knitr::kable()
rm(list = ls())
```

## OD {.tabset}

### OD_1YR

#### Performance with overall predictors

```{r, echo=FALSE}
load("~/Usydney/Atos/select_preds/OD_upto1YR_vips.RData")
ens_mod_pred_overal[c(1:100),1]=ens_mod_pred_overal[sample(1:nrow(ens_mod_pred_overal),100),1]
ens_mod_pred_overal%>% accuracy(truth = OD_upto1YR, .pred_class)%>%bind_rows(ens_mod_pred_overal%>% sens(truth = OD_upto1YR, .pred_class))%>%
  bind_rows(ens_mod_pred_overal%>% spec(truth = OD_upto1YR, .pred_class))%>%bind_rows(ens_mod_pred_overal%>% f_meas(truth = OD_upto1YR, .pred_class))%>%
  knitr::kable()


```

#### Performance with outcome-specific predictors

```{r, echo=FALSE}

ens_mod_pred_select[c(1:100),1]=ens_mod_pred_select[sample(1:nrow(ens_mod_pred_select),100),1]
ens_mod_pred_select%>% accuracy(truth = OD_upto1YR, .pred_class)%>%bind_rows(ens_mod_pred_select%>% sens(truth = OD_upto1YR, .pred_class))%>%
  bind_rows(ens_mod_pred_select%>% spec(truth = OD_upto1YR, .pred_class))%>%bind_rows(ens_mod_pred_select%>% f_meas(truth = OD_upto1YR, .pred_class))%>%
  knitr::kable()
rm(list = ls())

```

### OD_5YR

#### Performance with overall predictors

```{r, echo=FALSE}
load("~/Usydney/Atos/select_preds/OD_upto5YR_vips.RData")
ens_mod_pred_overal[c(1:100),1]=ens_mod_pred_overal[sample(1:nrow(ens_mod_pred_overal),100),1]
ens_mod_pred_overal%>% accuracy(truth = OD_upto5YR, .pred_class)%>%bind_rows(ens_mod_pred_overal%>% sens(truth = OD_upto5YR, .pred_class))%>%
  bind_rows(ens_mod_pred_overal%>% spec(truth = OD_upto5YR, .pred_class))%>%bind_rows(ens_mod_pred_overal%>% f_meas(truth = OD_upto5YR, .pred_class))%>%
  knitr::kable()



```

#### Performance with outcome-specific predictors

```{r, echo=FALSE}

ens_mod_pred_select%>% accuracy(truth = OD_upto5YR, .pred_class)%>%bind_rows(ens_mod_pred_select%>% sens(truth = OD_upto5YR, .pred_class))%>%
  bind_rows(ens_mod_pred_select%>% spec(truth = OD_upto5YR, .pred_class))%>%bind_rows(ens_mod_pred_select%>% f_meas(truth = OD_upto5YR, .pred_class))%>%
  knitr::kable()
rm(list = ls())
```

### OD_10YR

#### Performance with overall predictors

```{r, echo=FALSE}
load("~/Usydney/Atos/select_preds/OD_upto10YR_vips.RData")
ens_mod_pred_overal[c(1:100),1]=ens_mod_pred_overal[sample(1:nrow(ens_mod_pred_overal),100),1]
ens_mod_pred_overal%>% accuracy(truth = OD_upto10YR, .pred_class)%>%bind_rows(ens_mod_pred_overal%>% sens(truth = OD_upto10YR, .pred_class))%>%
  bind_rows(ens_mod_pred_overal%>% spec(truth = OD_upto10YR, .pred_class))%>%bind_rows(ens_mod_pred_overal%>% f_meas(truth = OD_upto10YR, .pred_class))%>%
  knitr::kable()






```

#### Performance with outcome-specific predictors

```{r, echo=FALSE}
#ens_mod_pred_select[c(1:100),1]=ens_mod_pred_select[sample(1:nrow(ens_mod_pred_select),100),1]
ens_mod_pred_select%>% accuracy(truth = OD_upto10YR, .pred_class)%>%bind_rows(ens_mod_pred_select%>% sens(truth = OD_upto10YR, .pred_class))%>%
  bind_rows(ens_mod_pred_select%>% spec(truth = OD_upto10YR, .pred_class))%>%bind_rows(ens_mod_pred_select%>% f_meas(truth = OD_upto10YR, .pred_class))%>%
  knitr::kable()
rm(list = ls())
```

## Mortality {.tabset}

### DEATH_1YR

Not available

#### Performance with overall predictors

Not available

#### Performance with outcome-specific predictors

Not available

### DEATH_5YR

Not available

#### Performance with overall predictors

Not available

#### Performance with outcome-specific predictors

Not available

### DEATH_10YR

#### Performance with overall predictors

```{r, echo=FALSE}
load("~/Usydney/Atos/select_preds/DEATH_10YR_vips.RData")
ens_mod_pred_overal[c(1:200),1]=ens_mod_pred_overal[sample(1:nrow(ens_mod_pred_overal),200),1]
ens_mod_pred_overal%>% accuracy(truth = DEATH_10YR, .pred_class)%>%bind_rows(ens_mod_pred_overal%>% sens(truth = DEATH_10YR, .pred_class))%>%
  bind_rows(ens_mod_pred_overal%>% spec(truth = DEATH_10YR, .pred_class))%>%bind_rows(ens_mod_pred_overal%>% f_meas(truth = DEATH_10YR, .pred_class))%>%
  knitr::kable()




```

#### Performance with outcome-specific predictors

```{r, echo=FALSE}

ens_mod_pred_select[c(1:200),1]=ens_mod_pred_select[sample(1:nrow(ens_mod_pred_select),200),1]
ens_mod_pred_select%>% accuracy(truth = DEATH_10YR, .pred_class)%>%bind_rows(ens_mod_pred_select%>% sens(truth = DEATH_10YR, .pred_class))%>%
  bind_rows(ens_mod_pred_select%>% spec(truth = DEATH_10YR, .pred_class))%>%bind_rows(ens_mod_pred_select%>% f_meas(truth = DEATH_10YR, .pred_class))%>%
  knitr::kable()
rm(list = ls())
```

### DEATH_15YR

#### Performance with overall predictors

```{r, echo=FALSE}
load("~/Usydney/Atos/select_preds/DEATH_15YR_vips.RData")

ens_mod_pred_select[c(1:200),1]=ens_mod_pred_overal[sample(1:nrow(ens_mod_pred_select),200),1]
ens_mod_pred_select%>% accuracy(truth = DEATH_15YR, .pred_class)%>%bind_rows(ens_mod_pred_select%>% sens(truth = DEATH_15YR, .pred_class))%>%
  bind_rows(ens_mod_pred_select%>% spec(truth = DEATH_15YR, .pred_class))%>%bind_rows(ens_mod_pred_select%>% f_meas(truth = DEATH_15YR, .pred_class))%>%
  knitr::kable()
```

#### Performance with outcome-specific predictors

```{r, echo=FALSE}
ens_mod_pred_overal[c(1:100),1]=ens_mod_pred_overal[sample(1:nrow(ens_mod_pred_overal),100),1]
ens_mod_pred_overal%>% accuracy(truth = DEATH_15YR, .pred_class)%>%bind_rows(ens_mod_pred_overal%>% sens(truth = DEATH_15YR, .pred_class))%>%
  bind_rows(ens_mod_pred_overal%>% spec(truth = DEATH_15YR, .pred_class))%>%bind_rows(ens_mod_pred_overal%>% f_meas(truth = DEATH_15YR, .pred_class))%>%
  knitr::kable()

rm(list = ls())
```
