---
title: "Atos Project"
output: rmdformats::readthedown
---

# Performance and Feature Importance Report

## An overview of this report

This report presents the performance and feature importance of prediction models of four outcomes:

-   Remission

-   Past month heroin use

-   OD

-   Mortality

    -   Please note that two shorter terms mortality outcomes were not included because of less than 20 cases.

```{r include=FALSE}
library(haven)
library(tidyverse)
library(tidymodels)
library(stacks)
library(vip)
library(pdp)
library(sparkline)
library(plotly)
```

## Past month heroin use {.tabset}

### HU_1YR

#### Performance

```{r, echo=FALSE}

load("~/Usydney/Atos/HU_1YR_vips.RData")
ens_mod_pred%>% accuracy(truth = HU_1YR, .pred_class)%>%
  bind_rows(ens_mod_pred%>% sens(truth = HU_1YR, .pred_class))%>%
  bind_rows(ens_mod_pred%>% spec(truth = HU_1YR, .pred_class))%>%
  bind_rows(ens_mod_pred%>% f_meas(truth = HU_1YR, .pred_class))%>%
  knitr::kable()


```

#### Feature Importance

```{r, echo=FALSE}
p=ggplot(vips,aes(x=reorder(Variable, importance),y=importance))+
  scale_fill_gradient(low = "green", high = "red") + 
  geom_bar(position="dodge", stat="identity", aes(fill = importance))+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+
  xlab("Predictor")+ ylab("Importance Rank")

ggplotly(p)
rm(list = ls())
```

### HU_5YR

#### Performance

```{r, echo=FALSE}
load("~/Usydney/Atos/HU_5YR_vips.RData")
ens_mod_pred%>% accuracy(truth = HU_5YR, .pred_class)%>%
  bind_rows(ens_mod_pred%>% sens(truth = HU_5YR, .pred_class))%>%
  bind_rows(ens_mod_pred%>% spec(truth = HU_5YR, .pred_class))%>%
  bind_rows(ens_mod_pred%>% f_meas(truth = HU_5YR, .pred_class))%>%
  knitr::kable()
```

#### Feature Importance

```{r, echo=FALSE}
p=ggplot(vips,aes(x=reorder(Variable, importance),y=importance))+
  scale_fill_gradient(low = "green", high = "red") + 
  geom_bar(position="dodge", stat="identity", aes(fill = importance))+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+
  xlab("Predictor")+ ylab("Importance Rank")

ggplotly(p)
rm(list = ls())
```

### HU_10YR

#### Performance

```{r, echo=FALSE}
load("~/Usydney/Atos/HU_10YR_vips.RData")
ens_mod_pred%>% accuracy(truth = HU_10YR, .pred_class)%>%
  bind_rows(ens_mod_pred%>% sens(truth = HU_10YR, .pred_class))%>%
  bind_rows(ens_mod_pred%>% spec(truth = HU_10YR, .pred_class))%>%
  bind_rows(ens_mod_pred%>% f_meas(truth = HU_10YR, .pred_class))%>%
  knitr::kable()

```

#### Feature Importance

```{r, echo=FALSE}
p=ggplot(vips,aes(x=reorder(Variable, importance),y=importance))+
  scale_fill_gradient(low = "green", high = "red") + 
  geom_bar(position="dodge", stat="identity", aes(fill = importance))+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+
  xlab("Predictor")+ ylab("Importance Rank")

ggplotly(p)
rm(list = ls())
```

## Remission {.tabset}

### STA_1YR

#### Performance

```{r, echo=FALSE}
load("~/Usydney/Atos/STA_1YR_vips.RData")
ens_mod_pred%>% accuracy(truth = STA_1YR, .pred_class)%>%
  bind_rows(ens_mod_pred%>% sens(truth = STA_1YR, .pred_class))%>%
  bind_rows(ens_mod_pred%>% spec(truth = STA_1YR, .pred_class))%>%
  bind_rows(ens_mod_pred%>% f_meas(truth = STA_1YR, .pred_class))%>%
  knitr::kable()

```


#### Feature Importance

```{r, echo=FALSE}
p=ggplot(vips,aes(x=reorder(Variable, importance),y=importance))+
  scale_fill_gradient(low = "green", high = "red") + 
  geom_bar(position="dodge", stat="identity", aes(fill = importance))+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+
  xlab("Predictor")+ ylab("Importance Rank")

ggplotly(p)
rm(list = ls())
```

### STA_5YR

#### Performance

```{r, echo=FALSE}
load("~/Usydney/Atos/STA_5YR_vips.RData")
ens_mod_pred%>% accuracy(truth = STA_5YR, .pred_class)%>%
  bind_rows(ens_mod_pred%>% sens(truth = STA_5YR, .pred_class))%>%
  bind_rows(ens_mod_pred%>% spec(truth = STA_5YR, .pred_class))%>%
  bind_rows(ens_mod_pred%>% f_meas(truth = STA_5YR, .pred_class))%>%
  knitr::kable()

```

#### Feature Importance

```{r, echo=FALSE}
p=ggplot(vips,aes(x=reorder(Variable, importance),y=importance))+
  scale_fill_gradient(low = "green", high = "red") + 
  geom_bar(position="dodge", stat="identity", aes(fill = importance))+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+
  xlab("Predictor")+ ylab("Importance Rank")

ggplotly(p)
rm(list = ls())
```

### MTA_5YR

#### Performance

```{r, echo=FALSE}
load("~/Usydney/Atos/MTA_5YR_vips.RData")
ens_mod_pred%>% accuracy(truth = MTA_5YR, .pred_class)%>%
  bind_rows(ens_mod_pred%>% sens(truth = MTA_5YR, .pred_class))%>%
  bind_rows(ens_mod_pred%>% spec(truth = MTA_5YR, .pred_class))%>%
  bind_rows(ens_mod_pred%>% f_meas(truth = MTA_5YR, .pred_class))%>%
  knitr::kable()


```

#### Feature Importance

```{r, echo=FALSE}
p=ggplot(vips,aes(x=reorder(Variable, importance),y=importance))+
  scale_fill_gradient(low = "green", high = "red") + 
  geom_bar(position="dodge", stat="identity", aes(fill = importance))+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+
  xlab("Predictor")+ ylab("Importance Rank")

ggplotly(p)
rm(list = ls())
```

### STA_10YR

#### Performance

```{r, echo=FALSE}
load("~/Usydney/Atos/STA_10YR_vips.RData")
ens_mod_pred%>% accuracy(truth = STA_10YR, .pred_class)%>%
  bind_rows(ens_mod_pred%>% sens(truth = STA_10YR, .pred_class))%>%
  bind_rows(ens_mod_pred%>% spec(truth = STA_10YR, .pred_class))%>%
  bind_rows(ens_mod_pred%>% f_meas(truth = STA_10YR, .pred_class))%>%
  knitr::kable()

```

#### Feature Importance

```{r, echo=FALSE}
p=ggplot(vips,aes(x=reorder(Variable, importance),y=importance))+
  scale_fill_gradient(low = "green", high = "red") + 
  geom_bar(position="dodge", stat="identity", aes(fill = importance))+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+
  xlab("Predictor")+ ylab("Importance Rank")

ggplotly(p)
rm(list = ls())
```

### MTA_10YR

#### Performance

```{r, echo=FALSE}
load("~/Usydney/Atos/MTA_10YR_vips.RData")
ens_mod_pred%>% accuracy(truth = MTA_10YR, .pred_class)%>%
  bind_rows(ens_mod_pred%>% sens(truth = MTA_10YR, .pred_class))%>%
  bind_rows(ens_mod_pred%>% spec(truth = MTA_10YR, .pred_class))%>%
  bind_rows(ens_mod_pred%>% f_meas(truth = MTA_10YR, .pred_class))%>%
  knitr::kable()

```

#### Feature Importance

```{r, echo=FALSE}
p=ggplot(vips,aes(x=reorder(Variable, importance),y=importance))+
  scale_fill_gradient(low = "green", high = "red") + 
  geom_bar(position="dodge", stat="identity", aes(fill = importance))+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+
  xlab("Predictor")+ ylab("Importance Rank")

ggplotly(p)
rm(list = ls())
```

### LTA_10yr

#### Performance

```{r, echo=FALSE}
load("~/Usydney/Atos/LTA_10yr_vips.RData")
ens_mod_pred%>% accuracy(truth = LTA_10yr, .pred_class)%>%
  bind_rows(ens_mod_pred%>% sens(truth = LTA_10yr, .pred_class))%>%
  bind_rows(ens_mod_pred%>% spec(truth = LTA_10yr, .pred_class))%>%
  bind_rows(ens_mod_pred%>% f_meas(truth = LTA_10yr, .pred_class))%>%
  knitr::kable()

```

#### Feature Importance

```{r, echo=FALSE}
p=ggplot(vips,aes(x=reorder(Variable, importance),y=importance))+
  scale_fill_gradient(low = "green", high = "red") + 
  geom_bar(position="dodge", stat="identity", aes(fill = importance))+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+
  xlab("Predictor")+ ylab("Importance Rank")

ggplotly(p)
rm(list = ls())
```

## OD {.tabset}

### OD_1YR

#### Performance

```{r, echo=FALSE}
load("~/Usydney/Atos/OD_upto1YR_vips.RData")
ens_mod_pred%>% accuracy(truth = OD_upto1YR, .pred_class)%>%
  bind_rows(ens_mod_pred%>% sens(truth = OD_upto1YR, .pred_class))%>%
  bind_rows(ens_mod_pred%>% spec(truth = OD_upto1YR, .pred_class))%>%
  bind_rows(ens_mod_pred%>% f_meas(truth = OD_upto1YR, .pred_class))%>%
  knitr::kable()

```

#### Feature Importance

```{r, echo=FALSE}
p=ggplot(vips,aes(x=reorder(Variable, importance),y=importance))+
  scale_fill_gradient(low = "green", high = "red") + 
  geom_bar(position="dodge", stat="identity", aes(fill = importance))+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+
  xlab("Predictor")+ ylab("Importance Rank")

ggplotly(p)
rm(list = ls())
```

### OD_5YR

#### Performance

```{r, echo=FALSE}
load("~/Usydney/Atos/OD_upto5YR_vips.RData")
ens_mod_pred%>% accuracy(truth = OD_upto5YR, .pred_class)%>%
  bind_rows(ens_mod_pred%>% sens(truth = OD_upto5YR, .pred_class))%>%
  bind_rows(ens_mod_pred%>% spec(truth = OD_upto5YR, .pred_class))%>%
  bind_rows(ens_mod_pred%>% f_meas(truth = OD_upto5YR, .pred_class))%>%
  knitr::kable()

```

#### Feature Importance

```{r, echo=FALSE}
p=ggplot(vips,aes(x=reorder(Variable, importance),y=importance))+
  scale_fill_gradient(low = "green", high = "red") + 
  geom_bar(position="dodge", stat="identity", aes(fill = importance))+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+
  xlab("Predictor")+ ylab("Importance Rank")

ggplotly(p)
rm(list = ls())
```

### OD_10YR

#### Performance

```{r, echo=FALSE}
load("~/Usydney/Atos/OD_upto10YR_vips.RData")
ens_mod_pred%>% accuracy(truth = OD_upto10YR, .pred_class)%>%
  bind_rows(ens_mod_pred%>% sens(truth = OD_upto10YR, .pred_class))%>%
  bind_rows(ens_mod_pred%>% spec(truth = OD_upto10YR, .pred_class))%>%
  bind_rows(ens_mod_pred%>% f_meas(truth = OD_upto10YR, .pred_class))%>%
  knitr::kable()

```

#### Feature Importance

```{r, echo=FALSE}
p=ggplot(vips,aes(x=reorder(Variable, importance),y=importance))+
  scale_fill_gradient(low = "green", high = "red") + 
  geom_bar(position="dodge", stat="identity", aes(fill = importance))+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+
  xlab("Predictor")+ ylab("Importance Rank")

ggplotly(p)
rm(list = ls())
```

## Mortality {.tabset}

### DEATH_1YR

Not available

#### Performance

Not available

#### Feature Importance

Not available

### DEATH_5YR

Not available

#### Performance

Not available

#### Feature Importance

Not available

### DEATH_10YR

#### Performance

```{r, echo=FALSE}
load("~/Usydney/Atos/DEATH_10YR_vips.RData")
ens_mod_pred%>% accuracy(truth = DEATH_10YR, .pred_class)%>%
  bind_rows(ens_mod_pred%>% sens(truth = DEATH_10YR, .pred_class))%>%
  bind_rows(ens_mod_pred%>% spec(truth = DEATH_10YR, .pred_class))%>%
  bind_rows(ens_mod_pred%>% f_meas(truth = DEATH_10YR, .pred_class))%>%
  knitr::kable()
```

#### Feature Importance

```{r, echo=FALSE}
p=ggplot(vips,aes(x=reorder(Variable, importance),y=importance))+
  scale_fill_gradient(low = "green", high = "red") + 
  geom_bar(position="dodge", stat="identity", aes(fill = importance))+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+
  xlab("Predictor")+ ylab("Importance Rank")

ggplotly(p)
rm(list = ls())
```

### DEATH_15YR

#### Performance

```{r, echo=FALSE}
load("~/Usydney/Atos/DEATH_15YR_vips.RData")
ens_mod_pred%>% accuracy(truth = DEATH_15YR, .pred_class)%>%
  bind_rows(ens_mod_pred%>% sens(truth = DEATH_15YR, .pred_class))%>%
  bind_rows(ens_mod_pred%>% spec(truth = DEATH_15YR, .pred_class))%>%
  bind_rows(ens_mod_pred%>% f_meas(truth = DEATH_15YR, .pred_class))%>%
  knitr::kable()
```

#### Feature Importance

```{r, echo=FALSE}
p=ggplot(vips,aes(x=reorder(Variable, importance),y=importance))+
  scale_fill_gradient(low = "green", high = "red") + 
  geom_bar(position="dodge", stat="identity", aes(fill = importance))+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+
  xlab("Predictor")+ ylab("Importance Rank")

ggplotly(p)
rm(list = ls())
```
